---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vtkr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/hypertidy/vtkr.svg?branch=master)](https://travis-ci.org/hypertidy/vtkr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hypertidy/vtkr?branch=master&svg=true)](https://ci.appveyor.com/project/hypertidy/vtkr)
<!-- badges: end -->

The goal of vtkr is to read data from files in [Visualization Toolkit format](https://en.wikipedia.org/wiki/VTK). 

Currently very WIP, but in time we can read in these models as rgl mesh forms. I don't know any other VTK reader
that's of use to R. If you do please let me know!

## TODO

* DONE Basic example read
* Support the structured points in ASCII form
* Support the triangles in BINARY form
* Get out the triangle CELLS attributes
* Generalize the functions to read header, points-only, detect format, etc. 
* Support more formats!

## Installation


You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hypertidy/vtkr")
```
## Example

This is a basic example to read an in-built VTK file. 

```{r example}
library(vtkr)
f <- system.file("extdata/STRUCTURED_GRID/volcano_points.vtk", package = "vtkr", mustWork = TRUE)
xyz <- read_vtk_points(f)
str(xyz)
```

Currently, we can only read 

* STRUCTURED_GRID POINTS (BINARY format) - we get a matrix of 3D coordinates
* UNSTRUCTURED_GRID POINTS triangles CELLS (ASCII format) - we get a list with 3D coordinates and triangle indices

No CELL attributes are yet read. 

Please get in touch!  I'm especially keen if you have example files that aren't supported yet.

---

  Please note that the 'vtkr' project is released with a
  [Contributor Code of Conduct](https://github.com/hypertidy/vtkr/blob/master/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
